Exploring the composition of lithic assemblages in Mesolithic south-eastern Norway

### 2021-05-04 analysis/paper/paper.Rmd
Working on implementing oxcaar for calibration and modelling of radiocarbon dates

h3 <- radiocarbon %>% 
  filter(site == "Hovland 3")

h3dat <- R_Date(h3$lab_code, h3$c14_bp, h3$error)
h3_sum <- oxcal_Sum(h3dat)
h3_run <- executeOxcalScript(h3_sum)
h3_text <- readOxcalOutput(h3_run)
h3_result <- parseFullOxcalOutput(h3_text)

oxcal_code <- paste(' Plot()
   {
    Sequence()
    {
     Boundary("Start");
     Phase()
     {',
      h3dat,
     '};
     Boundary("End");
    };
  };')
my_result_file <- executeOxcalScript(oxcal_code)
my_result_text <- readOxcalOutput(my_result_file)
my_result_data <- parseOxcalOutput(my_result_text)

my_oxcal_code <- ' Plot()
 {
  Sequence("Sequence1")
  {
   Boundary("Beginn");
   Phase("Phase1")
   {
    R_Date("Lab-1",5000,25);
    R_Date("Lab-2",4900,37);
   };
   Boundary("Between");
   Phase("Phase2")
   {
    R_Date("Lab-3",4800,43);
   };
   Boundary("End");
  };
 };'

>>>>

h3 <- radiocarbon %>% 
  filter(site == "Vallermyrene 1")

h3dat <- R_Date(h3$lab_code, h3$c14_bp, h3$error)

oxcal_code <- paste0('Plot()
   {
    Sequence()
    {
     Boundary("Start");
     Phase()
     {
    ',
      h3dat,
     '
     Sum("Vallermyrene 1");
     };
     Boundary("End");
    };
  };')
my_result_file <- executeOxcalScript(oxcal_code)
my_result_text <- readOxcalOutput(my_result_file)
my_result_data <- parseOxcalOutput(my_result_text, only.R_Date = FALSE)
plot(my_result_data$` Vallermyrene 1 `$posterior_probabilities$dates, my_result_data$` Vallermyrene 1 `$posterior_probabilities$probabilities, type = "l")

pst <- get_posterior_probabilities(my_result_data)
# h3_sum <- oxcal_Sum(h3dat)
# h3_run <- executeOxcalScript(h3_sum)
# h3_text <- readOxcalOutput(h3_run)
# h3_result <- parseFullOxcalOutput(h3_text)
